In infinity categories,
homotopy equivalent objects are equivalent by definition.
Therefore, the only well-defined notion of (co)limits 
is that of homotopy (co)limits.

Homotopy (co)limits behave very differently from ordinary (co)limits.
For example, the diagram
\[\begin{tikzcd}
    \{*,*\} \ar[r] \ar[d] \ar[dr,phantom,pos=.75,"\lrcorner"] & \{*\} \ar[d] \\
    \{*\} \ar[r] & S^1
\end{tikzcd}\]
is a homotopy pushout diagram of topological spaces,
where $\{*,*\}$ denotes the discrete space with two points.
The advantage of such a notion of (co)limits is that 
if we change the objects in the diagram to homotopy equivalent ones,
the result does not change.
The disadvantage is that they are difficult to compute.

However, model categories will give us great help in computing
homotopy (co)limits.

\subsection{Colimits and limits}

The simplest colimit is the empty colimit, that is, the initial object.
In ordinary category theory, the initial object is characterised by
the property that it admits a unique morphism to any other object.

The $\infty$-categorical way of saying something is unique 
is to say that all possible choices form a contractible space,
i.e.\ a contractible Kan complex.

\begin{definition}
    Let $\cat C$ be a quasi-category.
    An object $x\in\cat C$ is called an \term{initial object},
    if for any $y\in\cat C$, the mapping space $\Hom_{\cat C}(x,y)$ is contractible.
\end{definition}

The notation $\Hom_{\cat C}(x,y)$ refers to any one of
\[\Hom_{\cat C}^\vartriangleleft(x,y),\quad
\Hom_{\cat C}^\vartriangleright(x,y),\quad 
\Hom_{\mathfrak C\cat C}(x,y),\quad\text{etc.,} \]
which all have the same homotopy type (\ref{thm-5-h}).

\begin{remark}
    An initial object of $\cat C$
    is equivalently an initial object of the $\cat{hCW}$-enriched category $h\cat C$.
    In fact, most of the notions defined in this section will be equivalent to 
    the corresponding notions for $\cat{hCW}$-enriched categories. \varqed
\end{remark}

One may expect that initial objects are unique if they exist.
As before, uniqueness means being a contractible space.

\begin{lemma}
    Let $\cat{C}$ be a quasi-category, and let $x\in\cat{C}$.
    Then the maps 
    \[ \cat{C}_{x\/}\to\cat{C} \quad\text{and}\quad \cat{C}_{\/x}\to\cat{C} \]
    are a left fibration and a right fibration, respectively.
\end{lemma}

\begin{proof}
    Exercise for the reader.
\end{proof}

\begin{proposition}
    Let $\cat C$ be a quasi-category.
    \begin{itms}
        \item An object $x\in\cat C$ is an initial object, if and only if
        the left fibration
        \[ \cat C_{x\/}\to\cat C \]
        is a trivial fibration.
        \item The full subcategory spanned by the initial objects 
        is either empty, or a contractible Kan complex.
    \end{itms}
\end{proposition}

\begin{proof}
    For the first part, note that $x$ is an initial object 
    if and only if the map $\cat C_{x\/}\to\cat C$ has contractible fibres.
    But a left fibration has contractible fibres iff
    it is a trivial fibration, which is a standard fact \cite[Lemma~2.1.3.4]{htt}.

    For the second part, suppose we have a map $f\:\partial\Delta[n]\to\cat{C}$,
    such that all vertices are sent to initial objects, with $n>0$.
    We need to show that it can be extended to a map $\Delta[n]\to\cat{C}$.
    Then we may lift in the diagram 
    \[ \begin{tikzcd}
        \partial\Delta[n-1] \ar[d,"\cat{Cof}\ni"'] \ar[r,"f|_{\Lambda_0[n]}"] &
        \cat{C}_{f(0)\/} \ar[d,"\in\cat{Fib}\cap\cat{W}"] \\
        \Delta[n-1] \ar[r,"f|_{1\comma\dotsc\comma n}"'] \ar[ur,dashed] &
        \cat{C}
    \end{tikzcd} \]
    to get the desired extension of $f$ to $\Delta[n]$.
\end{proof}

Colimits are nothing but initial objects of under-categories.

\begin{definition}
    Let $\cat C$ be a quasi-category,
    $K$ a simplicial set,
    and let $f\:K\to\cat C$ be a diagram.
    A \term{colimit} of $f$ is an initial object of $\cat C_{K\/}$.
\end{definition}

We immediately deduce the following.

\begin{corollary}
    Let $\cat C$ be a quasi-category,
    $K$ a simplicial set,
    and let $f\:K\to\cat C$ be a diagram.
    \begin{itms}
        \item A map $\bar f\:K^\vartriangleright\to\cat C$
        is a colimit of $f$, if and only if
        the induced left fibration
        \[ \cat C_{K^\vartriangleright\/}\to\cat C_{K\/} \]
        is a trivial fibration.
        \item The category of colimits of $f$ 
        is either empty, or a contractible Kan complex.
    \end{itms}
\end{corollary}

\begin{proof}
    We have an isomorphism of simplicial sets
    \[ \cat C_{K^\vartriangleright\/}\simeq(\cat C_{K\/})_{x\/}, \]
    where $x$ denotes the image of the cone point of $K^\vartriangleright$.
    Everything else is clear.
\end{proof}

\begin{remark}\label{thm-6-c}
    The natural map 
    \[ \cat C_{K^\vartriangleright\/}\to\cat C_{x\/} \]
    is always a trivial fibration,
    as can be shown by verifying the lifting property,
    by transfinite induction on the number of simplices of $K$.
    Details are left to the reader. \varqed
\end{remark}

Colimits are not computable via this definition.
We need to deduce some of their properties to make them computable.

\begin{proposition}\label{thm-6-z}
    Let $\cat C$ be a quasi-category,
    and let $\{x_\alpha\}_{\alpha\in A}$ be a collection of objects in $\cat C$.
    An object $x\in\cat C$ is a coproduct of the objects $x_\alpha$,
    if and only if for any $y\in\cat C$, the induced map 
    \[ \Hom_{\cat C}(x,y)\to\prod_\alpha\Hom_{\cat C}(x_\alpha,y) \]
    is a homotopy equivalence.
\end{proposition}

\begin{proof}
    We have a map $A\to\cat{C}$, $\alpha\mapsto x_\alpha$.
    The right hand side is equivalent to  
    \[ \prod_\alpha{}(\cat C_{x_\alpha\/})_y
    \simeq (\cat C_{A\/})_y, \]
    where the subscript $y$ means taking the fibre of the map to $\cat C$.
    The left hand side is equivalent to 
    \[ (\cat C_{x\/})_y\simeq((\cat C_{A\/})_{x\/})_y \]
    by (\ref{thm-6-c}). Thus $x$ is a coproduct, if and only if the left fibration
    \[(\cat C_{A\/})_{x\/}\to\cat C_{A\/}\]
    is a trivial fibration,
    if and only if it has contractible fibres,
    if and only if all the left fibrations
    \[((\cat C_{A\/})_{x\/})_y\to(\cat C_{A\/})_y\]
    are trivial fibrations.
\end{proof}

This result on coproducts is a special case of a general theorem,
which we state below.

Let $\cat K$ be a category enriched over Kan complexes.
Then the category of simplicially enriched functors
\[ \operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet}) \]
carries two model structures:
\begin{itms}
    \item The \term{projective model structure},
    with weak equivalences and fibrations defined pointwise,
    and cofibrations defined by the lifting property.
    \item The \term{injective model structure},
    with weak equivalences and cofibrations defined pointwise,
    and fibrations defined by the lifting property.
\end{itms}
The constant functor
\[ \operatorname{const}\:\cat{sSet}\to\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet}) \]
is right Quillen with respect to the projective model structure,
and left Quillen with respect to the injective model structure.
Therefore, the colimit functor 
\[ \operatorname{colim}\:\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet})\to\cat{sSet} \]
is left Quillen with respect to the projective model structure,
as it is the left adjoint of the constant functor.
The limit functor 
\[ \operatorname{lim}\:\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet})\to\cat{sSet} \]
is right Quillen with respect to the injective model structure,
as it is the right adjoint of the constant functor.

\begin{definition}
    Let $\cat K$ be a category enriched over Kan complexes.
    \begin{itms}
        \item The \term{homotopy colimit} functor
        \[ \operatorname{hocolim}\:\Ho(\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet}))\to\Ho(\cat{sSet}) \]
        is the left derived functor of the left Quillen functor 
        \[ \operatorname{colim}\:\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet})\to\cat{sSet}, \]
        where $\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet})$
        is equipped with the projective model structure.

        \item The \term{homotopy limit} functor
        \[ \operatorname{holim}\:\Ho(\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet}))\to\Ho(\cat{sSet}) \]
        is the right derived functor of the right Quillen functor 
        \[ \operatorname{lim}\:\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet})\to\cat{sSet}, \]
        where $\operatorname{Fun}_{\cat{sSet}}(\cat K,\cat{sSet})$
        is equipped with the injective model structure.
    \end{itms}
\end{definition}

\begin{example}
    The homotopy pushout
    \[ \{*\}\underset{\{*,*\}}{\sqcup}\{*\} \]
    is the homotopy type of $S^1$, as is familiar in topology.
    A proof will be given later.
    \varqed
\end{example}

We can now use homotopy limits of simplicial sets 
to define homotopy (co)limits in categories enriched over Kan complexes.

Let $\cat K$ be a category enriched over Kan complexes.
We denote by $\cat K^\vartriangleright$ the $\cat{Kan}$-enriched category obtained
by adjoining a terminal object $\infty$, with 
\[ \Hom_{\cat K^\vartriangleright}(x,\infty)=\{*\}\quad(x\in\cat K^\vartriangleright),\quad
\Hom_{\cat K^\vartriangleright}(\infty,x)=\emptyset\quad(x\in\cat K).\quad  \]
Let $\cat K^\vartriangleleft$ be defined dually.

\begin{definition}
    Let $\cat C$ and $\cat K$ be categories enriched over Kan complexes,
    and let $f\:\cat K\to\cat C$ be a functor.
    \begin{itms}
        \item A \term{homotopy colimit} of $f$ is a functor 
        \[ \bar f\:\cat K^\vartriangleright\to\cat C, \]
        such that $\bar f|_{\cat K}=f$, and for any $y\in\cat C$, the induced map 
        \[ \Hom_{\cat C}(\bar f(\infty),y)\to\mathop{\operatorname{holim}}\limits_{k\in\cat K}\Hom_{\cat C}(f(k),y) \]
        is a weak homotopy equivalence.

        \item A \term{homotopy limit} of $f$ is a functor 
        \[ \bar f\:\cat K^\vartriangleleft\to\cat C, \]
        such that $\bar f|_{\cat K}=f$, and for any $y\in\cat C$, the induced map 
        \[ \Hom_{\cat C}(y,\bar f(\infty))\to\mathop{\operatorname{holim}}\limits_{k\in\cat K}\Hom_{\cat C}(y,f(k)) \]
        is a weak homotopy equivalence.
    \end{itms}
\end{definition}

This definition can be seen as the definition of $\infty$-(co)limits 
in the model of categories enriched over Kan complexes.
The following theorem states that
(co)limits in quasi-categories coincide with homotopy (co)limits in this sense.

\begin{theorem} \label{thm-6-x}
    Let $\cat C$ and $\cat K$ be categories enriched over Kan complexes,
    and let $f\:\cat K\to\cat C$ be a functor.
    Then the functor between quasi-categories
    \[ \mathfrak Nf\:\mathfrak N\cat K\to\mathfrak N\cat C \]
    has a (co)limit,
    if and only if $f$ has a homotopy (co)limit,
    and in this case, they coincide.
\end{theorem}

See \cite[Theorem~4.2.4.1]{htt}.

Of course, this also means that if $f\:\cat K\to\cat C$
is a functor of quasi-categories, then its (co)limits are computed by
the homotopy (co)limit of the functor
\[ R\mathfrak Cf\:R\mathfrak C\cat K\to R\mathfrak C\cat C \]
between $\cat{Kan}$-enriched categories.
This is because (co)limits are preserved by categorical equivalences.

\begin{example}
    When $\cat K=\Lambda_0[2]$, one has an isomorphism
    $\cat K^\vartriangleright\simeq\Delta[1]\times\Delta[1]$.
    The colimit of a diagram $\cat K\to\cat C$ is called a (homotopy) \term{pushout},
    which is a square in $\cat C$, i.e.\ a map $\Delta[1]\times\Delta[1]\to\cat C$.
    We denote pushouts by the usual notation $y\sqcup_xz$.
    By the theorem, we have 
    \[ \Hom_{\cat C}\bigl(y\underset{x}{\sqcup}z,w\bigr)\simeq
    \Hom_{\cat C}(y,w)\underset{\Hom_{\cat C}(x,w)}{\times}\Hom_{\cat C}(z,w) \]
    for any $w\in\cat C$,
    where the right hand side denotes a homotopy pullback of Kan complexes. 
    \varqed
\end{example}

As a corollary, we have the following criterion
that establishes certain ordinary pushouts as homotopy pushouts.

\begin{proposition}
    Let $\cat C$ be a simplicial model category.
    The ordinary pushout 
    \[ \begin{tikzcd}
        x\ar[r]\ar[d]\ar[dr,phantom,pos=.7,"\lrcorner"] & y\ar[d] \\
        z\ar[r] & y\underset{x}{\sqcup}z
    \end{tikzcd} \]
    coincides with the homotopy pushout,
    if the map $x\to y$ is a cofibration.
\end{proposition}

\begin{proof}[Sketch of Proof]
    The key is to show that the map 
    \[ \Hom_{\cat{C}}(y,w) \to \Hom_{\cat{C}}(x,w) \]
    is a fibration of simplicial sets,
    since it is known that an ordinary pullback along a fibration of simplicial sets 
    is a homotopy pullback.
    This will follow from the axioms of a simplicial model category 
    by a standard argument which we omit here.
\end{proof}

This gives an easy way to compute homotopy pushouts
in a simplicial model category. Namely,
to compute $y\sqcup_xz$, one finds a weak equivalence $y\to y'$,
such that the composition $x\to y\to y'$ is a cofibration.
Then the homotopy pushout $y\sqcup_xz$
is given by the ordinary pushout $y'\sqcup_xz$. For example,
in $\cat{Top}$, one has the homotopy pushout
\[ \{*\}\underset{X}{\sqcup}\{*\}\simeq\Sigma X. \]

\begin{remark}
    For simplicial model categories, 
    the $\infty$-categorical (co)limits coincide with 
    the derived functors of the (co)limit functors,
    provided that the projective and injective model structures exist.
    \varqed
\end{remark}

Finally, we mention a formula that computes homotopy (co)limits directly.
Readers unfamiliar with (co)ends may skip to the next subsection.

\begin{proposition}
    Let $f\:\cat K\to\cat C$ be a functor of $\cat{Kan}$-enriched categories.
    Assume that $\cat C$ is tensored and cotensored over $\cat{sSet}$.
    For example, this is always the case if $\cat C$ is a simplicial model category.
    
    \begin{itms}
        \item The homotopy colimit of $f$
        is computed by the simplicially enriched coend 
        \[ \operatorname{hocolim}f\simeq\int^{k\in\cat K}\mathfrak{N}(\cat K_{k\/})\otimes f(k), \]
        where $\otimes$ denotes the simplicial tensoring on $\cat C$.
        \item The homotopy limit of $f$ is computed by the simplicially enriched end
        \[ \operatorname{holim}f\simeq\int_{k\in\cat K}f(k)^{\mathfrak{N}(\cat K_{\/k})}, \]
        where the powering denotes the simplicial powering on $\cat C$.
    \end{itms}
\end{proposition}

See \cite{riehl}.

\begin{example}
    Let $G$ be a topological group acting on a space $X$.
    Then the \term{homotopy quotient} $X\/{}^{\mathrm h}G$ is defined by 
    \[ X\/{}^{\mathrm h}G:=(X\times EG)\/G, \]
    where $EG$ denotes the universal $G$-bundle over $BG$.
    This is exactly the homotopy colimit of the corresponding functor 
    \[ \cat{B}G\to\cat{Top}, \]
    where $\cat BG$ is the simplicial groupoid with a single object,
    whose mapping space is $\operatorname{Sing}G$. \varqed
\end{example}

\subsection{Adjoint functors}

Adjoint functors play a very important role
in classical category theory.
For example, colimits and limits are two special cases of adjoint functors.
For $\infty$-categories,
there is also a homotopical version of adjoint functors,
which we will now discuss.

\begin{definition}
    Let $\cat C,\cat D$ be quasi-categories, and let 
    \[ F\:\cat C\to\cat D,\quad G\:\cat D\to\cat C \]    
    be two functors. We say that $F$ and $G$ are a pair of 
    \term{adjoint functors} if there is an equivalence of functors 
    \[ \Hom_{\cat D}(F-,-)\simeq\Hom_{\cat C}(-,G-)\:\cat C\op\times\cat D\to\cat S. \]
    Precisely, we mean that the functors
    \[ \Hom_{\mathfrak C\cat D}(F-,-)\quad\text{and}\quad\Hom_{\mathfrak C\cat C}(-,G-) \]
    are weakly equivalent in the category 
    \[ \operatorname{Fun}_{\cat{sSet}}(\mathfrak C(\cat C\op\times\cat D),\cat{sSet}), \]
    equipped with the projective model structure.
\end{definition}

In order to understand the properties of adjoint functors,
we will formulate another two equivalent definitions.

\begin{definition}
    Let $\cat C$ be a quasi-category.
    
    \begin{itms}
        \item The quasi-category 
        \[ \mathscr P(\cat C):=\operatorname{Fun}(\cat C\op,\cat S) \]
        is called the category of \term{presheaves} on $\cat C$,
        where $\cat S:=\mathfrak N(\cat{Kan})$.
    
        \item The map
        \[\begin{aligned}
            Y\:\cat C&\to\mathscr P(\cat C),\\
            x&\mapsto h_x:=\Hom_{\cat C}(-,x)
        \end{aligned}\]
        is called the \term{Yoneda embedding}.
        Precisely, this map is defined by the simplicially enriched functor 
        \[\begin{aligned}
            \mathfrak C(\cat C\times\cat C\op)&\to\cat{Kan},\\
            (x,y)&\mapsto R\Hom_{\mathfrak C\cat C}(y,x)
        \end{aligned}\]
        by passing to the adjoint,
        where $R$ denotes the fibrant replacement.
    
        \item A presheaf on $\cat C$ is called \term{representable} if 
        it is equivalent to $h_x$ for some $x\in\cat C$.
    \end{itms}
\end{definition}

Via the Grothendieck construction (\ref{thm-5-gc}),
presheaves on $\cat C$ are equivalent to right fibrations over $\cat C$.
Namely, given $F\in\mathscr P(\cat C)$, the right fibration 
\[ \operatorname{Un}_{\cat C}F\to\cat C \]
has fibre (equivalent to) $F(x)$ at $x\in\cat C$.

\begin{definition}
    Let $\cat C$ be a quasi-category.
    A right fibration $X\to\cat C$ is \term{representable}, 
    if the presheaf 
    \[ \operatorname{St}_{\cat C}X\in\mathscr P(\cat C) \]
    is representable.
\end{definition}

By definition, representable right fibrations are of the form
$\operatorname{Un}_{\cat{C}}h_x$.
If we look at its fibres, we realise that it is equivalent to $\cat{C}_{\/x}$,
in the fibrewise sense, i.e.\ in $\cat{sSet}_{\/\cat{C}}$
with the contravariant model structure (\ref{thm-5-gc}).

\begin{proposition} \label{thm-6-rrf}
    Any representable right fibration over $\cat{C}$ is equivalent to 
    $\cat{C}_{\/x}$ in $\cat{sSet}_{\/\cat{C}}$,
    where $x\in\cat{C}$ is any representing object. \qed
\end{proposition}

Dually, a left fibration $p\:X\to\cat C$ is representable 
if the right fibration $p\op\:X\op\to\cat C\op$ is representable.

\begin{proposition}
    Let $\cat C$ be a quasi-category,
    and let $p\:\tilde{\cat C}\to\cat C$ be a right fibration.
    \begin{itms}
        \item $p$ is representable, if and only if $\tilde{\cat C}$
        has a terminal object.
        \item An object $x\in\cat C$ represents $p$,
        if and only if there exists a terminal object $\tilde x$ of $\tilde{\cat C}$,
        with $p(\tilde x)=x$.
    \end{itms}
    In particular, the full subcategory of $\cat C$
    spanned by the representing objects of $p$
    is either empty or a contractible Kan complex.
\end{proposition}

\begin{proof}
    We only need to prove the second part.

    Suppose $x$ represents $p$.
    Then $\tilde{\cat{C}}\simeq\cat{C}_{\/x}$ in $\cat{sSet}_{\/\cat{C}}$.
    The object $\mathbb{1}_x\in\cat{C}_{\/x}$ is terminal, as desired.

    Suppose such an object $\tilde{x}$ exists.
    It is a good exercise for the reader to show that the map
    \[ \tilde{\cat{C}}_{\/\tilde{x}} \to \cat{C}_{\/x} \]
    is a trivial fibration of simplicial sets.
    But since $\tilde{x}$ is terminal,
    we have another trivial fibration $\tilde{\cat{C}}_{\/\tilde{x}}\to\tilde{\cat{C}}$,
    which implies that 
    \[ \tilde{\cat{C}} \simeq \tilde{\cat{C}}_{\/\tilde{x}} \simeq \cat{C}_{\/x} \]
    as right fibrations over $\cat{C}$.
    Therefore, $p$ is represented by $x$.
\end{proof}

We can now give the equivalent definitions
of adjoint functors.

\begin{proposition} \label{thm-6-d}
    Let $\cat C,\cat D$ be two quasi-categories.
    Then a pair of adjoint functors between $\cat C$ and $\cat D$
    is equivalent to a left fibration 
    \[ p\:X\to\cat C\op\times\cat D, \]
    such that 
    \begin{itms}
        \item $p$ is \term{left representable}:
        for any $x\in\cat C$, the slice 
        \[ p|_{x\times\cat D}\:p^{-1}(x\times\cat D)\to x\times\cat D \]
        is a representable left fibration.
        \item $p$ is \term{right representable}:
        for any $y\in\cat D$, the slice 
        \[ p|_{\cat C\op\times y}\:p^{-1}(\cat C\op\times y)\to \cat C\op\times y \]
        is a representable left fibration.
    \end{itms}
    In fact, $p$ is given by the Grothendieck construction 
    of the functor
    \[ \Hom_{\cat D}(F-,-)\simeq\Hom_{\cat C}(-,G-)\:\cat C\op\times\cat D\to\cat S. \]
\end{proposition}

\begin{proof}
    Clearly, a pair of adjoint functor gives rise to such a left fibration $p$.

    Now suppose we are given such a left fibration $p$.
    Then for any $x\in\cat{C}$, we wish to define $Fx$ to be 
    a representing object of $p|_{x\times\cat{D}}$,
    or equivalently, an initial object of $p^{-1}(x\times\cat{D})$.
    This is done as follows.
    Consider the full subcategory $Y \subset X$ spanned by all such initial objects.
    One can prove that $Y\to\cat{C}\op$ is a trivial fibration
    (by repeated applications of the Grothendieck construction; the reader may try it),
    and we may take $F$ to be any of its sections.
    The functor $G$ is defined analogously.
\end{proof}

\begin{proposition}
    Let $\cat C,\cat D$ be two quasi-categories.
    Then a pair of adjoint functors between $\cat C$ and $\cat D$
    is equivalent to a map 
    \[ p\:M\to\Delta[1], \]
    such that 
    \begin{itms}
        \item There are categorical equivalences
        $p^{-1}(0)\simeq\cat C$ and $p^{-1}(1)\simeq\cat D$.
        \item $p$ is a cocartesian fibration.
        \item $p$ is a cartesian fibration.
    \end{itms}
    In fact, $M$ is given by $\mathfrak N\cat M$,
    where the $\cat{Kan}$-enriched category $\cat M$ is defined by 
    \begin{itms}
        \item Objects: pairs $(x,0)$ for $x\in\cat C$ and $(y,1)$ for $y\in\cat D$.
        \item Morphism spaces:
        \[ \begin{aligned}
            \Hom_{\cat M}((x,0),(y,0)) &:= \Hom_{R\mathfrak C\cat C}(x,y), \\
            \Hom_{\cat M}((x,1),(y,1)) &:= \Hom_{R\mathfrak C\cat D}(x,y), \\
            \Hom_{\cat M}((x,0),(y,1)) &:= \Hom_{R\mathfrak C\cat D}(Fx,y)\simeq\Hom_{R\mathfrak C\cat C}(x,Gy), \\
            \Hom_{\cat M}((x,1),(y,0)) &:= \emptyset.
        \end{aligned} \]
    \end{itms}
\end{proposition}

\begin{proof}
    Assume we are given $M$.
    Then it is straightforward to recover the adjoint pair, since (co)cartesian fibrations 
    give rise to transport functors, via the Grothendieck construction.

    It remains to show that this procedure is inverse to 
    the construction of $M$ in the formulation of the proposition.
    We omit these verifications.
\end{proof}

\begin{proposition}
    Let $\cat K,\cat C$ be quasi-categories.
    Suppose that every functor $\cat K\to\cat C$ has a colimit.
    Then the constant functor 
    \[ \operatorname{const}\:\cat C\to\operatorname{Fun}(\cat K,\cat C) \]
    admits a left adjoint, which is the colimit functor.
\end{proposition}

\begin{proof}
    We use the equivalent definition of adjoint functors given in (\ref{thm-6-d}).
    The functor $\operatorname{const}$ gives a right representable left fibration 
    \[ X \to \operatorname{Fun}(\cat K,\cat C)\op \times \cat{C}. \]
    It suffices to show that it is also left representable.
    But note that 
    \[ X|_{f\times\cat{C}} \simeq \cat{C}_{f\/}, \]
    and left representability is equivalent to $\cat{C}_{f\/}$ having an initial object,
    which is equivalent to $\cat{C}$ having colimits.
\end{proof}

\begin{remark}
    Let $\cat C,\cat D$ be simplicial model categories,
    and let $(F\dashv G)$ be a Quillen adjunction between them.
    Then $F$ and $G$ give rise to 
    a pair of adjoint functors between the quasi-categories
    $\mathfrak N(\cat C_{\mathrm{cf}})$ and
    $\mathfrak N(\cat D_{\mathrm{cf}})$. \varqed
\end{remark}
