\small
\begin{thebibliography}{MMMM}
    \itemsep=-.5ex
    
    \bibitem[GP74]{gp} Victor Guillemin and Alan Pollack (1974).
    \emph{Differential Topology}.
    Prentice-Hall.

    \bibitem[Hat01]{hatcher} Allen Hatcher (2001).
    \emph{Algebraic Topology}.
    Cambridge University Press.

    \bibitem[Hir76]{hirsch} Morris W. Hirsch (1976).
    \emph{Differential Topology}.
    Graduate Texts in Mathematics \textbf{33}. Springer.

    \bibitem[Lee12]{lee} John M. Lee (2012).
    \emph{Introduction to Smooth Manifolds}, 2ed.
    Graduate Texts in Mathematics \textbf{218}. Springer.

    \bibitem[Mat97]{matsu} Yukio Matsumoto (1997).
    \emph{An Introduction to Morse Theory},
    translated (2002) by K. Hudson and M. Saito.
    Translations of Mathematical Monographs \textbf{208}.
    AMS.

    \bibitem[Mil63]{milnor} John Milner (1963).
    \emph{Morse Theory}.
    Annals of Mathematics Studies \textbf{51}.
    Princeton University Press.

    \bibitem[Mil65]{milnor2} John Milner (1965).
    \emph{Lectures on the h-Cobordism Theorem}.
    Princeton University Press.

    \bibitem[MP12]{may} J.\,P. May and K. Ponto (2012).
    \emph{More Concise Algebraic Topology}.
    Chicago Lectures in Mathematics.
    University of Chicago Press.

    \bibitem[Sma61]{smale} Stephen Smale (1961).
    Generalized Poincar\'e's conjecture in dimensions greater than four.
    \emph{The Annals of Mathematics} \textbf{74} (2), 391--406.

    \bibitem[Sma62]{smale2} Stephen Smale (1962).
    On the structure of manifolds.
    \emph{American Journal of Mathematics} \textbf{84} (3), 387--399.

    \bibitem[Wal16]{wall} C.\,T.\,C. Wall (2016).
    \emph{Differential Topology}.
    Cambridge Studies in Advanced Mathematics \textbf{156}.
    Cambridge University Press.
\end{thebibliography}
